Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
minor rewording

One paper by Maheshwari et al.~\cite{Maheshwari_WSSSPE} that was
discussed was about the role of technological catalysts in overall e-research
process.  The paper focuses on ``technology catalysts" and their role in modern
scientific research process. Technology catalyst could be defined as a role
played by an individual with a know-how of technological advancements tasked
with user engagement with a goal of enacting scientific or engineering
applications using suitable tools and techniques to take advantage of
technological capabilities and benefiting applications.

One of the tasks of catalysts is to seek community collaborations for new
applications and user engagement thus benefiting both: science, by effective
running of scientific codes over computational infrastructure and technology,
by conducting research and seeking findings to improve technology.

>>>>

The paper by Maheshwari et al.~\cite{Maheshwari_WSSSPE} focuses on
``technology catalysts" and their role in the modern
scientific research process. Technology catalyst could be defined as a role
played by an individual with a know-how of technological advancements, tasked
with user engagement with a goal of enacting scientific or engineering
applications, and using suitable tools and techniques to take advantage of
technological capabilities and benefiting applications.

One of the tasks of catalysts is to seek community collaborations for new
applications and user engagement thus benefiting both: science, by effective
running of scientific codes on computational infrastructure, and technology,
by conducting research and seeking findings for technology improvement.
